---
title: "Temperature wrangling"
output: html_document
date: "2025-03-15"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# clear environment
rm(list = ls())

# load librarian (package for installing/loading packages)
if (!require("librarian")) install.packages("librarian")

# Load other necessary libraries
librarian::shelf(here, # relative file paths
                 tidyverse # data wrangling
)
```

# Bring in the data

Data for LTER 0 were sent by Tom Adam on January 27, 2025. Tom notes: "Here are the data from LTER0 10m.  There may be a couple of small data gaps (including ~ 1 week during July 2022) but otherwise I think this temperature record is mostly complete.  Let me know if you have any questions or if you discover any issues with the data."

Data for LTER 2 were downloaded online from the MCR data catalog by Julianna. Note from the metadata: "Beginning in July 2021 data are raw temperature values sampled every two minutes (SBE 39s and SBE 56s) or eight minutes (Onset HOBOs) depending on the instrument."

```{r read in data}
# LTER 0 data from Tom
lter0 <- read_csv(here("raw_data", "FOR00_BTM_10m_20170808_20240704.csv"))

# LTER 2 data from online data catalog
lter2 <- read_csv(here("raw_data", "MCR_LTER02_BottomMountThermistors_20230323.csv")) %>% 
  filter(reef_type_code == "FOR") %>% 
  filter(sensor_depth_m == 10) %>% 
  # only need the time around when we need to fill in LTER 0
  mutate(year = year(time_local)) %>% 
  filter(year > 2020 &
           year < 2023)

# photomosaic dates
photo_dates <- read_csv(here("raw_data", "photomosaic_dates.csv"))
```

# LTER 0

## Plot timeseries 

```{r}
lter0 %>% 
  ggplot(aes(x = time_utc, y = temperature_c)) +
  geom_line() # no obvious ones
```

## Look for gaps

```{r}
lter0 %>% 
  mutate(time_diff = lead(time_local) - time_local) %>%  
  # all time steps that are not 2 minutes
  filter(time_diff != make_difftime(num = 120)) %>% 
  group_by(time_diff) %>% 
  summarize(count = n()) 
  
```

See that we have a few types of gaps in the data:

- 1 weeklong gap
- 1 2-hour gap
- 165 four-minute gaps
- 44 gaps near 2 minutes but not exact
- 253,355 0 second gaps


What are all these 0 gaps?

```{r}
lter0 %>% 
  filter(time_local == as_datetime("2021-08-04 10:00:01")) # look like duplicates 

# are they all duplicates? get all the duplicates
lter0 %>% 
  mutate(time_diff = lead(time_local) - time_local) %>%  
  filter(time_diff == make_difftime(num = 0)) %>% 
  select(time_local) -> repeats

# see if they're all the same
lter0 %>% 
  filter(time_local %in% repeats$time_local) %>% 
  group_by(file_name, site, time_local, time_utc, reef_type_code, sensor_type, sensor_depth_m) %>% 
  summarize(sd = sd(temperature_c),
            count = n()) # YEP! All exact duplicates of 2... can just combine these
```

```{r combine zeros}
lter0 %>% 
  group_by(file_name, site, time_local, time_utc, reef_type_code, sensor_type, sensor_depth_m) %>% 
  summarize(temperature_c = mean(temperature_c)) -> lter0_2
  
```


**By far the biggest problem is the weeklong gap, which occurs on 2022-07-22 14:58:01**

- Gap starts at *2022-07-22 14:58:01*
- Gap ends at *2022-07-30 11:58:00* 


## Look for period around then in LTER 2 data

See if LTER 2 has the data missing from LTER 0

```{r}
lter2 %>% 
  mutate(month = month(time_local)) %>% 
  filter(year == 2022 &
           month == 7) %>% 
  select(site, time_local, sensor_type, temperature_c, year, month) -> lter2.07.22

# plot
lter2.07.22 %>% 
  ggplot(aes(x = time_local, y = temperature_c)) +
  geom_line()

```

Plot together with LTER 0 to see how similar they are

```{r}
# make LTER 0 in similar format
lter0_2 %>% 
  mutate(year = year(time_local),
         month = month(time_local)) %>% 
  filter(year == 2022 &
           month == 7) %>% 
  select(site, time_local, sensor_type, temperature_c, year, month) -> lter0.07.22

# join together
lter2.07.22  %>% 
  rbind(lter0.07.22) -> july2022
```

Plot together

```{r}
july2022 %>% 
  # plot time series
  ggplot(aes(x = time_local, y = temperature_c, color = site)) +
  geom_line() 
```

Actually differ more than I would have thought

```{r}
july2022 %>% 
  mutate(day = day(time_local),
         hour = hour(time_local)) %>% 
  group_by(site, day, hour) %>% 
  summarize(mean_temp = mean(temperature_c),
            count = n()) %>% 
  rename(day22 = day,
         hour22 = hour) %>% 
  # make new datetime column
  mutate(time_local_hr = (as_datetime(paste0("2022-07-", day22, " ", hour22, ":00:00")))) %>% 
  pivot_wider(names_from = site, values_from = mean_temp) %>% 
  # compare time series
  ggplot(aes(x = LTER00, y = LTER02, color = day22)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0)
```

Sometimes LTER 2 is higher and sometimes LTER 0 is, but it's relatively well correlated?

- More well correlated in the later part of the month, which is when the gap is (I think--July 22-30)

# Get hourly averages

To deal with weird gaps and also how how long it takes a water body to pass I think it makes sense to use hourly averages

```{r}
# get hourly averages for LTER 0
lter0_2 %>% 
  # make grouping variables
  mutate(yearGR = year(time_local),
         monthGR = month(time_local),
         dayGR = day(time_local),
         hourGR = hour(time_local)) %>%
  group_by(site, yearGR, monthGR, dayGR, hourGR) %>% 
  summarize(mean_hr_temp_c = mean(temperature_c),
            count = n()) -> lter0_3

# get hourly averages for LTER 2
lter2 %>% 
  # make grouping variables
  mutate(yearGR = year(time_local),
         monthGR = month(time_local),
         dayGR = day(time_local),
         hourGR = hour(time_local)) %>%
  group_by(site, yearGR, monthGR, dayGR, hourGR) %>% 
  summarize(mean_hr_temp_c = mean(temperature_c),
            count = n()) -> lter2_2
```

Get gaps from LTER2

```{r}
lter2_2 %>% 
  filter(yearGR == 2022 & monthGR == 7) %>% 
  filter(dayGR > 21 & dayGR < 31) -> lter2_3
```


month 7, day 22, hour 14 is the last full hour, then 7/30 with 12 hrs 

- Gap starts at *2022-07-22 14:58:01*
- Gap ends at *2022-07-30 11:58:00* 

Get rid of trailing bits on the 22nd and 30th

```{r}
lter0_3 %>% 
  # filter out missing partial days
  filter(!(yearGR == 2022 & monthGR == 7 & dayGR == 22)) %>% 
  filter(!(yearGR == 2022 & monthGR == 7 & dayGR == 30)) -> lter0_4
```

# Fill gap from LTER 0 with LTER 2 data

```{r}
lter0_4 %>% 
  rbind(lter2_3) %>% 
  # add datetime column back
  mutate(time_local_hr = (as_datetime(paste0(yearGR, "-", monthGR, "-", dayGR, " ", hourGR, ":00:00")))) -> lter0.2
```

Plot to see if it looks right

```{r}
lter0.2 %>% 
  filter(yearGR == 2022) %>% 
  # plot time series
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = site)) +
  geom_line() # looks right!
```

# Write CSV

```{r}
write_csv(lter0.2, here("cleaned_data", "hourlytemps_lter0_2.csv"))
```

# Get statistics for preceeding 6 months

## Averages

Need dates of when photomosaics were taken (approximately), which I found by looking on Grit under the `RECHARGE_Timeline`, `RECHARGE_Timeline_March_2022`, and `RECHARGE_Timeline_Aug2022` documents (want to take the last day of the time period)

- 7/20/2018 for 2018
- 8/4/2019 for 2019
- 8/21/2020 for 2020
- 7/29/2021 for 2021
- 7/23/2022 for 2022

```{r}
photo_dates %>% 
  mutate(photo_datetime = as_datetime(paste0(photo_year, "-", photo_month, "-", photo_day))) %>% 
  # get the date of the half year previous
  mutate(photo_6mo_date = photo_datetime - make_difftime(day = round(365/2))) %>% 
  # get the date of the 2 months previous
  mutate(photo_2mo_date = photo_datetime - make_difftime(day = round(365/6))) %>% 
  # get the date of the 10 months preceeding (can't do 12 because 2017 doesn't go back far enough)
  mutate(photo_10mo_date = photo_datetime - make_difftime(day = round(365/12*10))) -> photo_dates_2
```

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_6mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_6mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_6mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_6mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_6mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_6mo
```

Plot to make sure it worked

```{r}
lter0.2_6mo %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_6mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_6mo_temp = mean(mean_hr_temp_c)) -> mean_6mo
  
```

Get mean max 

```{r}
lter0.2_6mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint, yearGR, monthGR, dayGR) %>% 
  summarize(max_daily_temp = max(mean_hr_temp_c)) %>% 
  group_by(timepoint) %>% 
  summarize(mean_6mo_mean_max = mean(max_daily_temp)) -> mean_max_6mo
  
```

Compare

```{r}
mean_6mo %>% 
  full_join(mean_max_6mo) %>% 
  ggplot(aes(x = mean_6mo_temp, y = mean_6mo_mean_max)) +
  geom_point()
```

Exact same ordering

# Get statistics for preceeding 2 months

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_2mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_2mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_2mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_2mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_2mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_2mo
```

Plot to make sure it worked

```{r}
lter0.2_2mo %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_2mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_2mo_temp = mean(mean_hr_temp_c)) -> mean_2mo
  
```

Get mean max 

```{r}
lter0.2_2mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint, yearGR, monthGR, dayGR) %>% 
  summarize(max_daily_temp = max(mean_hr_temp_c)) %>% 
  group_by(timepoint) %>% 
  summarize(mean_2mo_mean_max = mean(max_daily_temp)) -> mean_max_2mo
  
```

Compare

```{r}
mean_2mo %>% 
  full_join(mean_max_2mo) %>% 
  ggplot(aes(x = mean_2mo_temp, y = mean_2mo_mean_max, color = timepoint)) +
  geom_point()
```

Compare with 6mo

```{r}
mean_2mo %>% 
  full_join(mean_6mo) %>% 
  ggplot(aes(x = mean_2mo_temp, y = mean_6mo_temp, color = timepoint)) +
  geom_point() # not related
```

# Get statistics for preceeding 10 months

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t0"), "photo_10mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t3"), "photo_10mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t6"), "photo_10mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t9"), "photo_10mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_2[grep(photo_dates_2$timepoint, pattern = "t12"), "photo_10mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_10mo
```

Plot to make sure it worked

```{r}
lter0.2_10mo %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_10mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_10mo_temp = mean(mean_hr_temp_c)) -> mean_10mo
  
```

Get mean max 

```{r}
lter0.2_10mo %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint, yearGR, monthGR, dayGR) %>% 
  summarize(max_daily_temp = max(mean_hr_temp_c)) %>% 
  group_by(timepoint) %>% 
  summarize(mean_10mo_mean_max = mean(max_daily_temp)) -> mean_max_10mo
  
```

Compare

```{r}
mean_10mo %>% 
  full_join(mean_max_10mo) %>% 
  ggplot(aes(x = mean_10mo_temp, y = mean_10mo_mean_max, color = timepoint)) +
  geom_point()
```

Compare with 6mo

```{r}
mean_10mo %>% 
  full_join(mean_6mo) %>% 
  ggplot(aes(x = mean_10mo_temp, y = mean_6mo_temp, color = timepoint)) +
  geom_point()
```

Compare with 2 mo

```{r}
mean_10mo %>% 
  full_join(mean_2mo) %>% 
  ggplot(aes(x = mean_10mo_temp, y = mean_2mo_temp, color = timepoint)) +
  geom_point() 
```

# Save CSV

```{r}
mean_6mo %>% 
  full_join(mean_2mo) %>% 
  write_csv(here("cleaned_data", "temperature_means.csv"))
```

# Robustness checks

## 6 months

Should try this with specific dates and with a general date (e.g., 8/20) and plot them against each other to see if we get the same relative hierarchy (don't want this to be too biased by when the photos were taken)

```{r}
photo_dates %>% 
  # try this with a specific date
  mutate(photo_datetime = as_datetime(paste0(photo_year, "-08-20"))) %>% 
  # get the date of the half year previous
  mutate(photo_6mo_date = photo_datetime - make_difftime(day = round(365/2))) %>% 
  # get the date of the 2 months previous
  mutate(photo_2mo_date = photo_datetime - make_difftime(day = round(365/6))) %>% 
  # get the date of the 10 months preceeding (can't do 12 because 2017 doesn't go back far enough)
  mutate(photo_10mo_date = photo_datetime - make_difftime(day = round(365/12*10))) -> photo_dates_3
```

Get the summaries

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_6mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_6mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_6mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_6mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_6mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_6mo_test
```

Plot to make sure it worked

```{r}
lter0.2_6mo_test %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_6mo_test %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_6mo_temp_test = mean(mean_hr_temp_c)) -> mean_6mo_test
  
```

Compare with 

```{r}
mean_6mo_test %>% 
  full_join(mean_6mo) %>% 
  ggplot(aes(x = mean_6mo_temp_test, y = mean_6mo_temp, color = timepoint)) +
  geom_point() 
```

## 2 months

Get the summaries

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_2mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_2mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_2mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_2mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_2mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_2mo_test
```

Plot to make sure it worked

```{r}
lter0.2_2mo_test %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_2mo_test %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_2mo_temp_test = mean(mean_hr_temp_c)) -> mean_2mo_test
  
```

Compare with 

```{r}
mean_2mo_test %>% 
  full_join(mean_2mo) %>% 
  ggplot(aes(x = mean_2mo_temp_test, y = mean_2mo_temp, color = timepoint)) +
  geom_point() 
```

## 10 months

Get the summaries

```{r}
lter0.2 %>% 
  ungroup() %>% 
  mutate(timepoint = case_when( # note: drop = TRUE is so it's not a tibble, just the real value
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t0"), "photo_10mo_date", drop = TRUE] ~ "t0",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t3"), "photo_10mo_date", drop = TRUE] ~ "t3",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t6"), "photo_10mo_date", drop = TRUE] ~ "t6",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t9"), "photo_10mo_date", drop = TRUE] ~ "t9",
    time_local_hr < photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_datetime", drop = TRUE] &
      time_local_hr > photo_dates_3[grep(photo_dates_3$timepoint, pattern = "t12"), "photo_10mo_date", drop = TRUE] ~ "t12",
    TRUE ~ "NA"
  )) -> lter0.2_10mo_test
```

Plot to make sure it worked

```{r}
lter0.2_10mo_test %>% 
  ggplot(aes(x = time_local_hr, y = mean_hr_temp_c, color = timepoint)) +
  geom_line() +
  geom_vline(xintercept = photo_dates_2$photo_datetime)
```

Get mean:

```{r}
lter0.2_10mo_test %>% 
  filter(timepoint != "NA") %>% 
  group_by(timepoint) %>% 
  summarize(mean_10mo_temp_test = mean(mean_hr_temp_c)) -> mean_10mo_test
  
```

Compare with 

```{r}
mean_10mo_test %>% 
  full_join(mean_10mo) %>% 
  ggplot(aes(x = mean_10mo_temp_test, y = mean_10mo_temp, color = timepoint)) +
  geom_point() 
```


